### 2021-07-10 submission.tex
latex set up

%%%%%%%%%%%%%%%%%
%   Problem 1   %
%%%%%%%%%%%%%%%%%
\part{Course Assignment Episode 1}

@@

$a_1 = x_1 \cdot w_{11}^1$
$b_1 = x_2 \cdot w_{21}^1$
$c_1 = x_3 \cdot w_{31}^1$

@@

$a_2 = x_1 \cdot w_{12}^1$
$b_2 = x_2 \cdot w_{22}^1$
$c_2 = x_3 \cdot w_{32}^1$

@@

$a_3 = h_1 \cdot w_{11}^2$
$b_3 = h_2 \cdot w_{21}^2$

@@

>>>>

\part{Course Assignment Episode 1}

@@

$a_1 = x_1 \cdot w_{11}^1 \; \;$
$b_1 = x_2 \cdot w_{21}^1 \; \;$
$c_1 = x_3 \cdot w_{31}^1 \; \;$

@@

$a_2 = x_1 \cdot w_{12}^1 \; \;$
$b_2 = x_2 \cdot w_{22}^1 \; \;$
$c_2 = x_3 \cdot w_{32}^1 \; \;$

@@

$a_3 = h_1 \cdot w_{11}^2 \; \;$
$b_3 = h_2 \cdot w_{21}^2 \; \;$

@@

\item 
	\begin{enumerate}[label = (\roman*)]
		\item
		$h_1=ReLu(1+1+1) = 3 \; \;$
		$h_2=ReLu(1+1+1) = 3 $

		$y=\sigma(3+3) \simeq 0.99753$

		\item
		$\frac{\partial L}{\partial \hat{y}} = \frac{-y}{\hat{y}}-\frac{1-y}{1-\hat{y}}\simeq -404 \; \; \;$

		$\frac{\partial y}{\partial d_3} = \sigma(d_3) \cdot (1-\sigma(d_3)) \simeq 0.00247 \; \; \;$

$\frac{\partial d_3}{\partial a_3} = 1 $

$\frac{\partial d_3}{\partial b_3} = 1 \; \; \;$

$\frac{\partial a_3}{\partial w_{11}^2} = h_1 = 3 \; \; \;$

$\frac{\partial b_3}{\partial w_{21}^2} = h_2 = 3 \; \; \;$

$\frac{\partial a_3}{\partial h_1} = w_{11}^2 = 1 $

$\frac{\partial b_3}{\partial h_2} = w_{21}^2 = 1 $

$\frac{\partial h_1}{\partial d_1} = 1 $

$\frac{\partial h_2}{\partial d_2} = 1 $

$\frac{\partial d_1}{\partial a_1} = 1 $

$\frac{\partial d_1}{\partial b_1} = 1 $

$\frac{\partial d_1}{\partial c_1} = 1 $

$\frac{\partial d_2}{\partial a_2} = 1 $

$\frac{\partial d_2}{\partial b_2} = 1 $

$\frac{\partial d_2}{\partial c_2} = 1 $

$\frac{\partial a_1}{\partial w_{11}^1} = 1 $

$\frac{\partial b_1}{\partial w_{21}^1} = 1 $

$\frac{\partial c_1}{\partial w_{31}^1} = 1 $

$\frac{\partial a_2}{\partial w_{12}^1} = 1 $

$\frac{\partial b_2}{\partial w_{22}^1} = 1 $

$\frac{\partial c_2}{\partial w_{32}^1} = 1 $

$\frac{\partial a_1}{\partial x_1} = 1 $

$\frac{\partial b_1}{\partial x_2} = 1 $

$\frac{\partial c_1}{\partial x_3} = 1 $

$\frac{\partial a_2}{\partial x_1} = 1 $

$\frac{\partial b_2}{\partial x_2} = 1 $

$\frac{\partial c_2}{\partial x_3} = 1 $

		\item
		$\frac{\partial L}{\partial \hat{y}} = \frac{-y}{\hat{y}}-\frac{1-y}{1-\hat{y}}\simeq -404 \; \; \;$

		\item
		$\Delta w_{ij} = -\eta \frac{\partial L}{\partial w_{ij}}$

		$\frac{\partial L}{\partial w_{11}^2} = \frac{\partial L}{\partial \hat{y}} \cdot \frac{\partial \hat{y}}{\partial d_3}  \cdot \frac{\partial d_3}{\partial w_{11}^2} = -0.99788$

$\Delta w_{11}^2 = 0.1 \cdot -0.99788 = -0.099788$

		$\frac{\partial L}{\partial w_{21}^2} = \frac{\partial L}{\partial \hat{y}} \cdot \frac{\partial \hat{y}}{\partial d_3}  \cdot \frac{\partial d_3}{\partial w_{21}^2} = -0.99788$

$\Delta w_{21}^2 = 0.1 \cdot -0.99788 = -0.099788$

		$\frac{\partial L}{\partial w_{11}^1} = \frac{\partial L}{\partial \hat{y}} \cdot \frac{\partial \hat{y}}{\partial d_3}  \cdot \frac{\partial d_3}{\partial a_3} \cdot \frac{\partial a_3}{\partial h_1 } \cdot \frac{\partial h_1}{\partial d_1} \cdot \frac{\partial d_1}{\partial a_1} \cdot \frac{\partial a_1}{\partial w_{11}^1} = -0.99788$

$\Delta w_{11}^1 = 0.1 \cdot -0.99788 = -0.099788$

Since the input values are the same and the weight values are also the same, the rest of the gradient changes have the same value. The calculation are analogous to the above ones.

	\item
	The symmetry of weights is not broken, so the hidden units can be replaced with a single unit producing the same output. The benefits of such solution are: faster training, more reliable model due to fewer parameters.

\section*{Question 4} 
\begin{enumerate}[label = (\alph*)]
    \item
    \begin{enumerate}[label = (\roman*)]
    \item
